Vaccines: Many Beliefs Study 3: Analysis

### 2019-04-30 notebooks/s1s2-pca-analysis.Rmd
re-run

cors <- df_preds %>%
  group_by(scale) %>%
  summarize(correlation = cor(predicted, observed))

@@

d_changes <- d_scored %>%
  filter(condition=="diseaseRisk") %>%
  spread(phase, mean) %>%
  mutate(change = post-pre) %>%
  select(-pre,-post) %>%
  group_by(scale) %>%
  summarize(meanChange = mean(change))

@@

pred_post %>%
  as_tibble() %>%
  gather(scale, response) %>%
  group_by(scale) %>%
  summarize(posttest = mean(response)) %>%
  left_join(
    (
      d_interv_pre %>%
  gather(scale,response) %>%
  group_by(scale) %>%
  summarize(pretest = mean(response))
    ), by = "scale"
  ) %>%
  mutate(change = posttest-pretest) -> pred_changes

>>>>

cors <- df_preds %>%
  group_by(scale) %>%
  summarise(correlation = cor(predicted, observed))

@@

d_changes <- d_scored %>%
  filter(condition=="diseaseRisk") %>%
  spread(phase, mean) %>%
  mutate(change = post-pre) %>%
  select(-pre,-post) %>%
  group_by(scale) %>%
  summarise(meanChange = mean(change))

@@

pred_post %>%
  as_tibble() %>%
  gather(scale, response) %>%
  group_by(scale) %>%
  summarise(posttest = mean(response)) %>%
  left_join(
    (
      d_interv_pre %>%
  gather(scale,response) %>%
  group_by(scale) %>%
  summarise(pretest = mean(response))
    ), by = "scale"
  ) %>%
  mutate(change = posttest-pretest) -> pred_changes

### 2019-04-30 notebooks/s2-analysis.Rmd
re-run

```{r}
devtools::source_gist(id = "f1994c0f8325abbc5d300600744af39d", filename="cbrm.R")

library(brms)
fit_ord <- cbrm(response ~ condition * phase + (1|workerId) + (1|question),
               data = d %>%
                    filter(scale=="vaccIntent") %>%
                    mutate(
                      condition = relevel(condition, ref="noInterv"),
                      response = response + 4),
               family=cumulative(),
               control = list(adapt_delta = .85),
               cores = parallel::detectCores(),
               iter = 2000,
               cached_file = "fit_ord.rds")
summary(fit_ord)
```

@@

```{r}
fit_ord2 <- cbrm(post ~ condition + preMean + (1|workerId) + (1|question),
               data=d1,
               family=cumulative(),
               control = list(adapt_delta = .85),
               cores = parallel::detectCores(),
               iter = 2000,
               cached_file = "fit_ord2.rds")
summary(fit_ord2)
```

>>>>

```{r}
# devtools::source_gist(id = "f1994c0f8325abbc5d300600744af39d", filename="cbrm.R")
# 
# library(brms)
# fit_ord <- cbrm(response ~ condition * phase + (1|workerId) + (1|question),
#                data = d %>%
#                     filter(scale=="vaccIntent") %>%
#                     mutate(
#                       condition = relevel(condition, ref="noInterv"),
#                       response = response + 4),
#                family=cumulative(),
#                control = list(adapt_delta = .85),
#                cores = parallel::detectCores(),
#                iter = 2000,
#                cached_file = "fit_ord.rds")
# summary(fit_ord)
```

@@

```{r}
# fit_ord2 <- cbrm(post ~ condition + preMean + (1|workerId) + (1|question),
#                data=d1,
#                family=cumulative(),
#                control = list(adapt_delta = .85),
#                cores = parallel::detectCores(),
#                iter = 2000,
#                cached_file = "fit_ord2.rds")
# summary(fit_ord2)
```
